msc dissertation

### 2021-08-04 msc dissertation code.Rmd
latest

install.packages("effectsize")
library(effectsize)

cohens_d(pennystudy2r1)

@@

#Find out the sum for each type of news in different condition
p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, FUN = sum)

@@

#since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
ggplot(p1, aes(x = condition, y = measurement/428, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/428, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```
### graph 2 attention check above and equal to 1

@@

@@

#since the obs is 1664, thus 1664/2 = 832 participants. So to get percentage of sharing intention each fake and real news need to divided by 832/2 = 416
ggplot(p2, aes(x = condition, y = measurement/416, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/416, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```

@@

#Find out the sum for each type of news in different condition
p3 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3, FUN = sum)

@@

#since the obs is 1292 for attention > 2, thus 1292/2 = 646 participants. So to get percentage of sharing intention each fake and real news need to divided by 646/2 = 323
ggplot(p3, aes(x = condition, y = measurement/323, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/323, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```

>>>>

#calculate the effect size cohen's d
##since they need to compare true vs false headline in different condition, thus, create a new data frame that only contain treatment and control with the attention check above and equal to 2, as stated in the research

install.packages("effsize")
library(effsize)

pennys2r1a2cohen <- subset(pennystudy2r1, dummycheck %in% c("2","3"))
pennys2r1a2cohenc <- subset(pennys2r1a2cohen, condition %in% c("0"))
pennys2r1a2cohent <- subset(pennys2r1a2cohen, condition %in% c("1"))

cohen.d(pennys2r1a2cohenc$Fake, pennys2r1a2cohenc$Real, na.rm = TRUE)
cohen.d(pennys2r1a2cohent$Fake, pennys2r1a2cohent$Real, na.rm = TRUE)

#condition vs measurement

pennys2r1a2cohenc <- subset(pennys2r1longa2, condition %in% c("0"))
pennys2r1a2cohent <- subset(pennys2r1longa2, condition %in% c("1"))

cohen.d(pennys2r1a2cohenc$condition, pennys2r1a2cohenc$measurement, na.rm = TRUE)
cohen.d(pennys2r1a2cohent$condition, pennys2r1a2cohent$measurement, na.rm = TRUE)

@@

#Find out the sum for each type of news in different condition

p1 <- aggregate(measurement~condition+newstype, data = pennystudy2plot1, na.rm = TRUE, FUN = sum)
p1 <- transform(p1, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/428, 4)*100)))

@@

#since the obs is 1712, thus 1712/2 = 856 participants. So to get percentage of sharing intention each fake and real news need to divided by 856/2 = 428
ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```
### graph 2 attention check above and equal to 1

@@

#separating the sheet

pennystudy2plot2c <- subset(pennystudy2plot2, condition %in% c("0"))
pennystudy2plot2t <- subset(pennystudy2plot2, condition %in% c("1"))

@@

#since the obs is 1664, thus 1664/2 = 832 participants. So to get percentage of sharing intention each fake and real news need to divided by 832/2 = 416
ggplot(p2, aes(x = condition, y = measurement/428, fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = round(measurement/428, digits = 3)), vjust = 1.5, position = position_dodge(0.9))+
    scale_y_continuous(labels = scales::percent)
```

@@

#Find out the sum for each type of news in different condition

p3 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3, na.rm = TRUE, FUN = sum)
p3 <- transform(p3, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/428, 4)*100)))

@@

#plot the graph under the proportion of overall observation (856)
ggplot(p3, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```
### graph 3 attention check above and equal to 2: mean
```{r, message=FALSE}
#condition 3: above and equal to 2
pennystudy2plot3 <- pennys2r1longa2 %>%
  select (c(1, 2, 3, 4))

pennystudy2plot3c <- subset(pennystudy2plot3, condition %in% c("0"))
pennystudy2plot3t <- subset(pennystudy2plot3, condition %in% c("1"))

#Find out the sum and percentage for each type of news in each condition

##control, percentage = 658/2 = 329
p31 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3c, na.rm = TRUE, FUN = sum)
p31 <- transform(p31, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/329, 4)*100)))

##treatment, percentage = 634/2 = 317
p32 <- aggregate(measurement~condition+newstype, data = pennystudy2plot3t, na.rm = TRUE, FUN = sum)
p32 <- transform(p32, percent = ave(measurement, condition, FUN = function(x) paste0(round(x/317, 4)*100)))

#merge two table together under same column name
p3 <- rbind(p31,p32)

#plot the graph
ggplot(p3, aes(x = condition, y = as.numeric(percent), fill = newstype)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```
